\documentclass[12pt, american]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\pagestyle{plain}
\usepackage{float}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{relsize}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{adjustbox}
\usepackage{enumitem}
\usepackage{titletoc}
\usepackage[page,header]{appendix}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup[table]{skip=2pt}
\usepackage{lmodern}
\usepackage{wrapfig}  
\usepackage{array}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[figuresright]{rotating}
\usepackage{tabularx}
\usepackage{framed}
\usepackage{longtable}
\usepackage[flushleft]{threeparttable}
\usepackage{color}
\usepackage{hyperref}  
\usepackage{hhline}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{threeparttablex}
\usepackage{txfonts}
\hypersetup{
  colorlinks=true,
  citecolor={blue},
urlcolor={blue},
linkcolor ={blue}}
\newcommand{\RowColor}{\rowcolor{cyan!30}} 
\newtheorem{define}{Definition}
\newtheorem{hypo}{Hypothesis}
\newtheorem{ass}{Assumption}
\usepackage{bibentry}
\usepackage{longtable}
\usepackage{tikz}
\usepackage{tikz-qtree,tikz-qtree-compat}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes.multipart}
\usepackage{CJKutf8}
\usepackage[overlap, CJK]{ruby}
\newenvironment{SChinese}{
\CJKfamily{gkai}
\CJKtilde
\CJKnospace}{}
\newcommand{\cntxt}[1]{\begin{CJK}{UTF8}{}\begin{SChinese}#1\end{SChinese}\end{CJK}}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs, threeparttable, siunitx}
\newcommand{\sym}[1]{\ifmmode^{#1}\else\textsuperscript{#1}\fi} % ← only if you keep \sym
\usepackage{fancyvrb}        % already in most modern templates
\newtheorem{prop}{Proposition}
\newtheorem{hyp}{Hypothesis}
\usepackage{babel,csquotes}
\usepackage[natbib,authordate,sorting=nyt,sortcites=true,dashed=false,uniquename=false,citetracker=false,
  ibidtracker=false,]{biblatex-chicago}
\AtEveryBibitem{\clearlist{language}}
\AtEveryBibitem{\clearfield{month}}
\addbibresource{paper.bib}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}

% --------------------------------------------------
% COLOR BOX + CODE
% --------------------------------------------------
\usepackage[minted,most]{tcolorbox}  % load tcolorbox ONCE, with the minted library
\usepackage{minted}                  % pygments interface
\usepackage{newunicodechar}          % map any stray UTF‑8 chars

% ----  Unicode fixes (curly quotes + real minus sign)  ----
\newunicodechar{−}{\ensuremath{-}}  % U+2212
% \newunicodechar{“}{``}% opening dbl quote
% \newunicodechar{”}{''}% closing  dbl quote
% \newunicodechar{’}{'} % apostrophe / closing sgl quote
% after \usepackage{CJK}
\makeatletter
% when \bfseries is requested inside CJK, use the 'hei' family instead of bold 'gkai'
\renewcommand\CJKbold{\CJKfamily{hei}}
\makeatother

\usepackage{tocloft}
\cftsetpnumwidth{4em}   % set enough space for page numbers
\cftsetrmarg{5em}       % adjust right margin to match


% --------------------------------------------------
% GLOBAL BOX STYLE
% --------------------------------------------------
\tcbset{
  colframe      = blue!80!black,
  boxrule       = 0.85pt,
  sharp corners,
  enhanced
}
\newcommand{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{Var}
% --------------------------------------------------
% PROMPT‑STYLE BOX DEFINITION
% --------------------------------------------------


% The pre-analysis plan registration can be found here:   \url{https://doi.org/10.17605/OSF.IO/2XH9E}

% acknowledgment: Molly Roberts, Victor Shih, Tongtong Zhang  Iza Ding  2024 scholar 

\title{\textbf{Posting Like a State:\\ How do Citizens Interact with Autocrats'  Media
}}\author{ Gary Ziwen Zu\thanks{Ph.D. candidate, Department of Political Science, UCSD. Email: \href{mailto:zzu@ucsd.edu}{zzu@ucsd.edu}.} }
\date{\today}		


\begin{document}

\hypersetup{pageanchor=false}
\maketitle
\thispagestyle{empty}

  \begin{abstract}
  \noindent How should scholars interpret engagement with official media in authoritarian settings? Existing accounts often read digital traces on state platforms either as evidence of propaganda success or as noise generated by skeptical audiences. I argue instead that official accounts are mixed channels that bundle public service information with political messaging, and that citizens sort their responses according to the visibility of the expressive act. Using 4.29 million posts from 329 Chinese local-government WeChat accounts, I first show that public service content dominates citizen attention, creating an attention dilemma: service information helps governments build durable audiences for future political communication while crowding out overt propaganda at the moment of consumption. I then exploit two interface reforms that changed the meaning of a click. The 2018 redesign collapsed low-visibility likes and rebundled approval with socially legible recommendation, sharply reallocating reactions across channels. The 2020 return of the like button provides cleaner causal leverage: like rates jump for hard and soft propaganda, while public-signal rates remain flat. These findings recast engagement metrics as strategic behavioral traces rather than direct measures of regime support and extend preference falsification theory to layered digital expression.

\vspace{0.2in}

\noindent \textbf{Keywords}: digital authoritarianism; propaganda; official social media; WeChat; preference falsification; state--society interaction.

 \end{abstract}



\doublespacing
\newpage
\hypersetup{pageanchor=true}
\newcolumntype{x}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\setcounter{page}{1} 
\renewcommand{\thepage}{\arabic{page}}

\begin{refsection}

\section{Introduction}

How do citizens in autocracies interact with official social media, and what do those traces actually mean? As propaganda, public communication, and service delivery migrate onto digital platforms, state-controlled accounts accumulate vast numbers of reads, likes, and shares. These metrics are tempting to interpret as indicators of propaganda success or regime support. Yet in authoritarian settings, interacting with official content is rarely a purely expressive act. Citizens may engage because they need information, because a post is difficult to avoid, because approval is low-cost, or because visible endorsement carries reputational and political risk. The political meaning of digital engagement is therefore fundamentally ambiguous.

Existing work speaks to pieces of this puzzle, but rarely to the mechanism at stake here. Research on Chinese propaganda shows that the party-state competes for attention through commercialization, soft propaganda, distraction, and popularization rather than relying on crude indoctrination alone \parencite{Brady2008,KingPanRoberts2017,LuPan2021,MattinglyYao2022,RepnikovaFang2018,Roberts2018,Stockmann2013,Wang2024Propaganda,Zou2021}. Research on preference falsification and self-censorship emphasizes the gap between private belief and public expression under pressure \parencite{CarterCarterSchick2024,JiangYang2016,Kuran1995,NoelleNeumann1993,ShenTruex2020}. A third literature shows that government WeChat accounts are not merely propaganda outlets: local authorities also use them for public service delivery, routine contact, and audience acquisition \parencite{JiangEtAl2021,LiuMaXia2024,YuShen2026,Zheng2013,ZhengZheng2014}. A related strand highlights semi-official accounts, delegated censorship, and layered platform governance, suggesting that state influence is often embedded in organizationally ambiguous or platform-native forms \parencite{Neagli2021,SunZhao2022,TaiFu2020}. What these literatures do not yet explain well is how platform design changes the political meaning of interaction itself.

I argue that official social media in digital authoritarianism are mixed channels that bundle public service information with political messaging, and that citizens sort their behavior across different levels of expressive risk. On WeChat, reading is low-risk consumption, a like is low-visibility approval, \textit{zaikan} is socially legible endorsement, and sharing is the highest-visibility form of amplification. This layered-expression perspective shifts the theoretical question away from whether citizens ``believe'' propaganda and toward how they manage observable traces of alignment.

I evaluate this argument using 4.29 million posts published by 329 prefecture-level government WeChat official accounts between 2013 and early 2025. The article makes two empirical moves. First, I use a theory-driven `LLM + human' classification workflow to assign fine-grained post labels and then collapse them into three main content families: hard propaganda, soft propaganda, and public service. Second, I exploit the 2018 and 2020 WeChat interface reforms as discontinuities that changed what a click meant. The 2018 redesign bundled approval with public recommendation; the 2020 redesign restored a lower-visibility like button alongside \textit{zaikan}.

Three findings organize the paper. Public service content dominates attention, creating an attention dilemma: the content that helps governments build durable audiences is not the content that looks most overtly political. The 2018 redesign sharply contracts low-visibility likes and reallocates reactions into a more socially legible channel. The 2020 return of likes provides cleaner causal leverage: like rates jump for hard and soft propaganda, while public-signal rates remain flat. Official engagement metrics are therefore better understood as strategic behavioral traces than as transparent measures of regime support.

This article makes three contributions. First, it extends preference falsification theory from speech to platform-mediated behavior by showing that digital expression is layered across reading, liking, \textit{zaikan}, and sharing. Second, it contributes to the study of propaganda and media consumption by separating attention from endorsement and by showing how service content both builds and competes for political attention. Third, it recasts official social media as an everyday site of authoritarian state--society interaction, where governments manage not only information but also the terms under which citizens can safely engage.

\section{Theory and Hypotheses}

Official social media in authoritarian settings should be understood as a platformed interaction regime rather than as a simple channel of state persuasion. In classic preference falsification accounts, the central distinction is between private preference and public statement. On platforms such as WeChat, however, expression is not binary. The interface decomposes response into multiple actions that expose users to different audiences and therefore to different expressive risks. The state may observe aggregate traces, but friends, colleagues, and acquaintances can also infer meaning from visible acts. Digital preference falsification is therefore layered: the same user may privately consume official content, register low-visibility approval, and avoid socially visible endorsement \parencite{Kuran1995,NoelleNeumann1993,ShenTruex2020,TsaiMen2018,Xu2022WeChat}.

This layered-expression logic matters because Chinese government WeChat accounts are mixed channels rather than purely political outlets. Existing research shows that state agencies use social media not only to disseminate political messages but also to provide services, route transactions, manage crises, and sustain routine interaction with the public \parencite{JiangEtAl2021,LiuMaXia2024,YuShen2026,Zheng2013,ZhengZheng2014}. That literature is especially useful because it shows that many users approach official accounts as lookup tools or service interfaces rather than as ideological venues. Service content therefore helps governments build durable audiences, normalize repeated contact, and increase the probability that users encounter future political content. At the moment of consumption, however, service information also competes with overt political messaging for scarce attention. This is the paper's attention dilemma.

The same logic also changes how we should think about propaganda. Contemporary influence online often works through participatory persuasion, semi-official intermediaries, and delegated forms of control rather than through a single visible propaganda apparatus \parencite{KingPanRoberts2017,LuPan2021,Neagli2021,RepnikovaFang2018,SunZhao2022}. Hard propaganda foregrounds hierarchy, ideology, discipline, and coercive state capacity. Soft propaganda packages regime-favorable messages in more appealing, emotionally resonant, or developmental frames \parencite{MattinglyYao2022,PanShaoXu2022,Wang2024Propaganda}. Citizens may read all three kinds of content, but the willingness to leave an observable trace should vary with both content risk and interface design. Platform reforms do not merely change aesthetics. They reprice the political and social costs of interacting with the state.

This framework yields four expectations:

\noindent \textbf{H1 (Attention and Utility).} Public service content should attract more routine consumption than either hard or soft propaganda because it provides immediate utility and lower expressive stakes.

\noindent \textbf{H2 (Rebundling Visible Approval).} When the 2018 redesign bundles approval with public recommendation, low-visibility like responses should collapse and observed reactions should be reallocated into more socially legible channels.

\noindent \textbf{H3 (Private Substitution).} When low-visibility likes return in 2020, approval should shift back toward likes rather than rising uniformly across all public-facing reactions.

\noindent \textbf{H4 (Political-Risk Gradient).} These reallocations should be strongest for hard propaganda, then soft propaganda, and weakest for routine public-service content.

\begin{table}[htbp]
\centering
\small
\caption{Platform reforms and theoretical expectations}
\label{tab:policy_timepoints}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.4cm} >{\raggedright\arraybackslash}X >{\centering\arraybackslash}p{1.55cm} >{\centering\arraybackslash}p{1.8cm} >{\centering\arraybackslash}p{1.55cm}}
\toprule
\textbf{Time point} & \textbf{Brief policy content} & \textbf{\shortstack{Reading /\\ exposure}} & \textbf{\shortstack{Visible\\ endorsement}} & \textbf{\shortstack{Low-risk\\ approval}} \\
\midrule
2017--05 (v6.5.8 rollout) &
WeChat introduces ``See'' (\textit{kanyikan}), adding a friend- and algorithm-based discovery channel while leaving the bottom ``like'' button unchanged. &
$+$ &
$0$ &
$0$ \\
\midrule
2018--12--21 &
WeChat 7.0 replaces ``like'' with ``good-looking'' (\textit{haokan}, later \textit{zaikan}), bundling approval with recommendation into ``See'' (\textit{kanyikan}). &
$0$ &
\shortstack{reallocated\\ / ambiguous} &
$-$ \\
\midrule
2020--06--29 &
The ``like'' button is restored at the bottom of public-account articles alongside the existing ``seen'' (\textit{zaikan}) and share buttons. &
$0$ &
$0 / -$ &
$+$ \\
\bottomrule
\end{tabularx}
\vspace{2pt}

\begin{minipage}{\textwidth}
\footnotesize \textit{Note:} `+' indicates an expected increase, `-' an expected decrease, and `0' little immediate change. The 2018 redesign mechanically rebundles approval with recommendation, so observed public-signal measures may be reallocated rather than move with a single clean sign. The strongest directional effects are expected for hard propaganda.
\end{minipage}
\end{table}


\section{Setting, Data, and Measurement}

WeChat is the central digital infrastructure of everyday life in China. Since its launch in 2011, it has evolved into a multipurpose ``super app'' that combines messaging, payments, news distribution, and social networking within a single platform. By the 2020s, it had become the primary interface through which Chinese citizens communicate, consume news, and access digital public and private services. For a study of official digital communication in China, WeChat matters not because it is just another social media platform, but because it is deeply embedded in ordinary social, administrative, and economic life \parencite{Ng2015,Roberts2020}.

Within this ecosystem, ``public accounts'' operate as mixed institutional channels. They transmit propaganda and political messaging, publicize leadership priorities, and provide highly practical information and service announcements \parencite{JiangEtAl2021,LiuMaXia2024,YuShen2026,Zheng2013,ZhengZheng2014}. At the same time, the broader WeChat ecosystem includes semi-official and organizationally ambiguous accounts that can carry state-aligned messages without looking fully official \parencite{Neagli2021}. A typical article displays a read counter together with several engagement mechanisms: a like button, \textit{haokan}/\textit{zaikan}, sharing, collecting, and comments. These buttons do not measure the same thing with different labels. They ask users to leave different kinds of traces under different conditions of visibility.

The key institutional changes are the 2018 and 2020 interface reforms. In December 2018, WeChat replaced the original like button on newly pushed public-account articles with a ``good-looking'' button tightly integrated with the ``See'' tab. A previously quasi-private like was transformed into a socially legible recommendation. In June 2020, WeChat restored the traditional like button alongside \textit{zaikan} and sharing, thereby unbundling low-visibility approval from public recommendation. I treat 2017 as background discovery reform and 2018/2020 as the two main discontinuities for expressive engagement. Table~\ref{tab:policy_timepoints} summarizes these shifts.

This study uses the universe of posts published by 329 prefecture-level government WeChat public accounts between January 2013 and early January 2025, covering 31 provincial-level units and 4,287,179 posts. The unit of observation for classification is the individual post. For each post, I record the account identifier, publication date, title, full article text, and engagement indicators displayed in the interface, including reads, likes, shares, comments, and \textit{haokan}/\textit{zaikan}. Because WeChat top-codes some counters at 100,000 (displayed as ``100k+''), I recode those values to 100,001 so they remain ordered while preserving censoring at the upper bound.

To categorize post content at scale, I use OpenAI's GPT-5.1 as a text coder rather than as a generator. The model receives the Chinese title and full article text, but not engagement outcomes, account identifiers, or indicators for the reform periods. The coding workflow is built on a fixed ten-category taxonomy and a transparent normalization layer for raw labels. The main text relies on this workflow only for measurement credibility; Appendix A reconstructs the taxonomy-construction process and the raw-label normalization rules that organize the released corpus, while later appendix sections document validation and diagnostic checks.

I validate the LLM labels against an independently coded gold-standard sample of 2,000 posts labeled by trained research assistants using the same codebook. The appendix reports the full reliability protocol, aggregate validation metrics, and category-level confusion matrix. For the main analyses, I collapse the fine-grained labels into three theoretically motivated families: hard propaganda, soft propaganda, and public service. Hard propaganda includes overtly political and disciplinary content; soft propaganda packages regime-favorable messages through development, culture, tourism, and performance narratives; public service covers instrumental governance content such as procedures, welfare, health, traffic, weather, and emergency guidance. State-governance and uncoded residual categories remain in the data for balance checks and appendix material but are not the paper's main theoretical families.

The paper's measurement logic is therefore theory-driven rather than purely unsupervised. The LLM solves the assignment problem at the post level; it does not decide which families matter theoretically. That distinction is important because the theoretical categories come from prior literature on mixed governance communication, soft propaganda, and expressive visibility rather than from an inductive topic model alone. I use topic modeling only as a supplementary audit. Appendix D uses BERTopic, STM, and manual review of residual clusters to assess whether low-confidence or residual posts reveal a substantively important missed family. The purpose of those diagnostics is to stress-test the coding scheme, not to replace it.

\section{Descriptive Findings}

The descriptive evidence establishes three facts that motivate the causal analysis. First, official WeChat feeds are genuinely mixed channels. Across the full corpus, public service is the largest of the three main families with about 1.37 million posts, followed by soft propaganda with 1.16 million posts and hard propaganda with 0.95 million posts. Governments are not using these accounts only to broadcast ideology; they are also using them to solve everyday informational problems.

Second, attention is even more skewed toward service content than production is. Public service posts receive about 432 average reads, compared with roughly 218 for soft propaganda and 135 for hard propaganda. Public service therefore draws more than three times the average readership of hard propaganda. This is the paper's attention dilemma: the content that makes official accounts useful and sticky is also the content that crowds out overtly political messaging at the moment of consumption.

Third, reaction profiles shift sharply around interface changes. Like rates collapse after the 2018 redesign and public-signal rates rise across all three main families, indicating that a once-private trace has been rebundled into a more socially legible recommendation channel. When likes return in 2020, like rates recover while public-signal rates do not exhibit corresponding jumps. The descriptive patterns therefore already suggest that the interface changes the form of engagement more than the underlying presence of attention.

\section{Research Design}

The main empirical strategy is a local linear regression discontinuity design centered on the two interface reforms that directly changed the meaning of approval: 21 December 2018 and 1 July 2020. I aggregate the data to day-by-content-group cells and estimate discontinuities in five outcomes: reads per post, like rates, \textit{zaikan} rates, public-signal rates (shares plus \textit{zaikan}), and total reaction rates. The running variable is days from the cutoff. All specifications use local linear fits with post-count weights and a one-year window around the reform.

I also report two simple robustness checks. First, I re-estimate the main specifications using a narrower 180-day bandwidth and a seven-day donut around the cutoff. Second, I examine continuity in post volume and each content group's daily share of total posting. These checks matter because the 2018 redesign changes the observable meaning of approval itself, while the 2020 redesign more cleanly restores an additional low-visibility channel.

This difference in institutional interpretation matters for how I read the estimates. The 2018 discontinuity is informative about rebundling and expressive reallocation, but it is not a clean test of net endorsement because the button semantics change. The 2020 discontinuity is the cleaner causal test of private substitution: it restores a low-visibility channel while leaving higher-visibility channels in place. The strongest causal claims therefore come from whether approval moves back into likes without a parallel jump in public-signal outcomes.

\section{Causal Findings}

The 2018 redesign behaves like a rebundling shock. Across hard propaganda, soft propaganda, and service content, low-visibility like rates fall sharply at the cutoff. The robust local-linear estimates are about $-0.0098$ for hard propaganda, $-0.0129$ for soft propaganda, and $-0.0079$ for service. At the same time, \textit{zaikan} and public-signal rates jump: for hard propaganda the public-signal estimate is about $+0.0068$, for soft propaganda about $+0.0068$, and for service about $+0.0037$. Read counts per post show no clear discontinuity. Substantively, once approval is bundled with public recommendation, observable reactions are reallocated into a more socially legible channel rather than disappearing altogether.

The 2020 redesign is cleaner and more directly speaks to layered expression. When WeChat restores the like button, like rates jump for all three main families, but the increase is largest for hard propaganda ($+0.0046$), followed by soft propaganda ($+0.0039$), and then service ($+0.0031$). By contrast, public-signal rates around the same cutoff are statistically flat for hard propaganda, soft propaganda, and service. For hard and soft propaganda, total reaction rates also rise, while service shows a smaller and less precise change. This is the paper's main causal result: when a lower-visibility approval channel returns, citizens use it, especially for political content, without producing an equivalent increase in more public-facing endorsement.

The 2020 results also help separate attention from endorsement. Reads per post do not increase for hard or soft propaganda and actually decline for service content at the cutoff. Whatever else is changing in 2020, the core discontinuity is not a sudden demand shock for official information. It is a reallocation of approval into a lower-risk expressive form.

\section{Heterogeneity}

The clearest heterogeneity is by content risk. The 2020 like-rate rebound follows the expected ordering from the theory: hard propaganda reacts most strongly, soft propaganda next, and service least. This ranking is consistent with the claim that the political meaning of an observable trace matters most when the underlying content is overtly political.

At the same time, the continuity checks caution against treating every discontinuity symmetrically. Around the 2018 redesign, hard-propaganda post volume and posting share exhibit some discontinuity, which makes the 2018 estimates best read as evidence of expressive rebundling rather than a standalone clean causal effect. Around the 2020 redesign, continuity is considerably cleaner for hard propaganda and service, while soft-propaganda posting share shifts more noticeably. The strongest identification therefore comes from the comparison between hard propaganda and service at the 2020 cutoff.

Taken together, these heterogeneities sharpen the substantive interpretation. Platform reforms do not affect all state content equally. They matter most when citizens are asked to leave politically interpretable traces and when the interface offers meaningful choice between safer and riskier forms of assent.

\section{Conclusion}

Official engagement metrics on authoritarian platforms are not transparent measures of support. They are shaped by mixed content environments and by the visibility structure of the interface itself. On WeChat, public service content sustains attention and builds durable audiences, while interface design determines how safely citizens can convert attention into approval.

The broader implication is that digital authoritarian control works partly by structuring traces, not only by changing beliefs. Once we distinguish low-risk consumption from low-visibility approval and from socially legible endorsement, the political meaning of a click changes. That insight extends preference falsification theory to platform-mediated behavior and suggests a more cautious reading of engagement metrics in authoritarian settings.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage                  % start bibliography on a new page
\begingroup               % keep spacing changes local to the bib only
  \singlespacing          % force single-line spacing inside the bibliography
  \setlength\bibitemsep{0pt}  % zero extra vertical space between entries
  \printbibliography
\endgroup





\end{refsection}

\newpage

\appendix

\section*{Online Supplemental Information}
\doublespacing
\startcontents[sections] \printcontents[sections]{l}{1}{\setcounter{tocdepth}{3}}
\setcounter{page}{0} 
\thispagestyle{empty}
\newpage
\renewcommand{\thepage}{SI-\arabic{page}}
\setcounter{figure}{0} 
\renewcommand{\thefigure}{SI.\arabic{figure}}     
\setcounter{table}{0} 
\renewcommand{\thetable}{SI.\arabic{table}}

\section{Taxonomy Construction}\label{app:taxonomy}
This appendix documents the taxonomy-construction logic used to organize the instructional WeChat corpus. Because the released dataset already contains settled post-level category assignments, the appendix is written as an instructor-prepared reconstruction of a plausible discovery phase rather than as a claim about ex ante fieldwork. The goal is to show transparently how the final ten-category codebook, higher-order analytic families, and raw-label normalization rules can be motivated from the observed corpus. In practical terms, the current released category is treated as the settled endpoint of the workflow, and the discovery sample is drawn retrospectively to document how that endpoint can be justified and audited.

\subsection{Instructor-prepared reconstruction of the discovery phase}\label{app:taxonomy-discovery}
The raw instructional corpus contains 4,287,179 posts and 877 distinct raw category strings. Table~\ref{tab:taxonomy-overview} shows that exact matches to the ten final canonical labels already cover 98.41 percent of the corpus, leaving a residual raw-label pool of only 1.59 percent. In other words, the reconstruction problem is not to discover hundreds of equally plausible topic classes. It is to explain how a large corpus with a concentrated label structure can be reviewed, normalized, and documented in a way that yields a stable codebook.

\input{../tables/taxonomy_summary_overview.tex}

To reconstruct that process, I draw an instructor-prepared discovery sample of 400 posts from the released corpus. The sample is designed to maximize coverage of both settled labels and normalization problems. It includes 25 posts from each of the ten canonical labels, 75 posts from the largest substantive residual label translated as \textit{party discipline and clean government}, 25 posts from the most common service-label variant translated as \textit{public service information (variant)}, and 50 posts from the remaining residual pool. This design yields immediate exposure to the stable core of the taxonomy while still forcing coders to confront the kinds of lexical drift and boundary cases that make normalization necessary in practice. Table~\ref{tab:taxonomy-discovery-sample} reports the realized design.

\input{../tables/taxonomy_discovery_sample_design.tex}

In the reconstructed workflow, two coders with journalism or local-media backgrounds review this discovery sample first. Their task is not to optimize machine performance. It is to identify whether the released labels cohere into a manageable set of recurring communicative types and to flag where the raw labels differ only lexically from categories that are already substantively present. The discovery phase therefore serves three functions at once: documenting the dominant label structure, identifying normalization candidates, and writing the decision rules that define the final codebook.

\subsection{Codebook generation}\label{app:taxonomy-codebook}
The reconstructed discovery review yields a ten-category canonical codebook. These labels are the final detailed categories used in the instructional dataset: ideology and propaganda education, current-affairs and leadership activity, public-service information, social security and public welfare, emergency management and risk communication, policy and government disclosure, social governance and law-enforcement bulletins, mass mobilization and social participation, economic and development construction, and city image and cultural activities. Table~\ref{tab:taxonomy-canonical-distribution} shows their exact-match prevalence in the raw corpus.

\input{../tables/taxonomy_canonical_distribution.tex}

The higher-order analytic families used in the main text are generated by collapsing these ten detailed labels according to communicative purpose and expressive risk. Ideology and leadership activity form \textit{hard propaganda}; service, welfare, and emergency posts form \textit{public service}; policy disclosure, governance bulletins, and participation campaigns form \textit{state governance}; and development plus city-image posts form \textit{soft propaganda}. Table~\ref{tab:taxonomy-family-mapping} records that mapping explicitly. This coding structure preserves a fine-grained layer for discovery and auditing while keeping the theory-facing families compact enough for the main empirical analysis.

\input{../tables/taxonomy_family_mapping.tex}

This reconstruction also clarifies why the final codebook is not simply a topic model relabeled by hand. The detailed categories are stable because they correspond to recurring communicative functions in local-government posting, not because they exhaust all semantic variation in the corpus. The appendix therefore treats the ten labels as a practical codebook for organizing the released data and the four higher-order families as the theory-facing layer used in the article's hypotheses and heterogeneity tests.

\subsection{Normalization of raw labels}\label{app:taxonomy-normalization}
The long tail of raw labels is dominated by a very small number of high-frequency variants rather than by a large number of substantively distinct missed classes. Table~\ref{tab:taxonomy-top-residual-labels} shows that the residual label translated as \textit{party discipline and clean government} alone accounts for 92.96 percent of the residual raw-label pool, while the residual label translated as \textit{public service information (variant)} accounts for another 2.95 percent. The remaining residual labels are scattered across small lexical variants, narrow topical phrases, and genuinely uninformative strings such as \textit{unclassified}.

\input{../tables/taxonomy_top_residual_labels.tex}

The normalization rule in the reconstructed workflow is intentionally conservative. High-frequency and substantively obvious lexical variants are collapsed into an existing canonical label. Near-synonyms such as the service-label variant are mapped into the canonical public-service label; word-order reversals such as \textit{cultural activities and city image} are mapped into \textit{city image and cultural activities}; and party-discipline labels such as \textit{party discipline and clean government} are folded into \textit{ideology and propaganda education} because they function as explicit political-discipline content rather than as a separate service or governance category. Labels that remain too ambiguous after lexical inspection, such as broad environmental strings without a clear service, governance, or development orientation, are retained as residual rather than being forced into a canonical class. Table~\ref{tab:taxonomy-normalization-examples} illustrates the normalization logic used in the reconstruction.

\input{../tables/taxonomy_normalization_examples.tex}

The point of this appendix is therefore procedural and documentary. It shows how one can begin with a corpus that already has settled instructional labels, extract a discovery sample, reconstruct the codebook-building logic, and make the normalization layer explicit enough that later human validation and LLM-based full-corpus assignment rest on a transparent measurement scaffold.

\clearpage
\section{Human Validation Protocol and Reliability}\label{app:human}
This appendix documents the human-coding procedure used to construct the gold-standard validation set and to benchmark model performance.

\subsection{Sampling design for the validation set}\label{app:sampling}
The validation set consists of a stratified sample of 2,000 posts drawn from the full corpus after preprocessing. The appendix should report the stratification directly and explain how it improves coverage of rare categories and boundary cases without changing the benchmark's inferential role.

\subsection{RA training, instructions, and coding interface}\label{app:training}
Research assistants use the same substantive coding guide as the LLM-facing codebook, together with a short training protocol and examples of boundary cases. The appendix should document the training sequence, coding interface, and adjudication rules for ambiguous posts.

\subsection{Constructing the reference label and inter-coder reliability}\label{app:reliability}
The reference label should be constructed transparently, either by majority rule plus adjudication for ties or by a pre-specified adjudication protocol. Reliability should be reported with an appropriate multi-coder statistic such as Krippendorff's alpha or Fleiss' kappa before comparing the model to the human benchmark.

\clearpage
\section{Model Performance}\label{app:performance}
This appendix reports category-level classification performance and diagnostic summaries.

\subsection{Aggregate metrics}\label{app:aggmetrics}
The main text should report only the aggregate performance statistics needed for measurement credibility. This appendix should report the full micro- and macro-averaged precision, recall, and F1 metrics for the final frozen classifier.

\subsection{Category-level metrics and confusion matrix}\label{app:confusion}
This appendix should also include per-category precision, recall, and F1 together with the full confusion matrix or a corresponding heatmap. Those diagnostics are important because the paper's theoretical claims depend on distinguishing hard propaganda, soft propaganda, and public service from neighboring boundary categories.

\clearpage
\section{Topic-Model Robustness and Residual Topic Audit}\label{app:topic}
This appendix explains how topic models are used as a supplementary discovery and robustness exercise rather than as the source of the paper's main categories.

\subsection{Why topic models remain supplementary}\label{app:topiclogic}
The paper's main measurement strategy is theory-driven: the politically relevant families are specified conceptually before large-scale coding. Topic models therefore serve a different purpose. They help assess whether the residual or low-confidence posts conceal a substantively important missing family and whether the main categories mask sharp semantic drift over time or space.

\subsection{BERTopic and STM diagnostics}\label{app:topicmodels}
The appendix should report parallel diagnostics from BERTopic and from a more classical structural topic model. The goal is not to replace the LLM labels, but to examine whether the residual topic structure primarily subdivides the existing families or instead reveals a coherent omitted class that should be incorporated into the codebook.

\subsection{Human review of candidate clusters}\label{app:topichuman}
Any residual cluster flagged by BERTopic or STM should be manually reviewed. The appendix should report the cluster size, dominant terms, representative posts, and the coding decision that follows from human inspection: map the cluster into an existing family, retain it as residual, or justify a new analytic category if and only if it is substantively large and theoretically distinct.




\singlespacing


\end{document}
